An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/intro.tex
ruzica

@@

Second, without templates, learning rules and constraints is 
another challenge.
Rather than relying on pre-defined templates or 
manually correcting training set,
we introduce and perform probabilistic learning approaches 
on probabilistically typed representations
generated in the transformation phase.
The learning process first analyzes the occurrences of each pair
of entries in the training set, 
then computes the likelihood that each pair can constitute a rule, 
and finally derive many rules.

Compared with previous efforts,
\app does not only rely on users' templates, it learns the rules about  
and is capable of detecting intricate configuration errors that
cannot be identified by existing work (details in $\S$\ref{sec-motiv}).

>>>>

Finally, we checks whether a
given variable

@@

Second, when learning rules we use very general templates to 
infer them. The user does not need to provide any templates -- they are internally associated to the types.
Nevertheless, in addition to those general templates, we still need specific algorithms to learn
rules that cannot be easily templated.

### 2016-05-10 OSDI/trans.tex
ruzica

The responsibility of the translator is to transform a given sample
dataset of configuration files into another set of files written in
typed and well-structured representations.
The translator can be seen a parser, and it is only
used to generate an intermediate representation for the post
process, such as learning rules (see $\S$\ref{sec-learn}).
Coupled with rules generated by learner module,
we will have a complete language model to verify configuration files
of our interest.

>>>>

The translator takes as input a sample dataset of configuration files and transforms a given sample
dataset of configuration files into another set of files written in
typed and well-structured representations.
The translator can be seen a parser, and it is only
used to generate an intermediate representation for the post
process, such as learning rules (see $\S$\ref{sec-learn}).
Coupled with rules generated by learner module,
we will have a complete language model to verify configuration files
of our interest.
